---
title: "inco15-reshaping"
author: "Gianna Lampert"
date: "2023-11-28"
output: html_document
---
Repo(repository): a place wehre the VC keeps the project files and their history
Branch: parallel version of the project 

Lets put this up to github!

```{r}
library(tidyverse)
```
Cleaning long-form data 
 -each observation is a row, each variable is a column 
 -each column is a variable and each row is different 
 - ex. each line represents a unique combination of country and year 

Wide form data
- plots can be harder to make
```{r}
gdp <- read_delim("../../data/oecd-gdp.csv.bz2")
gdp %>% 
  head()
```
```{r}
gdpLong <- 
  gdp %>% 
  pivot_longer(!c(country, indicator),
               names_to = "year",
               values_to = "gdp")
gdpLong %>% 
  head(10)
```
```{r}
gdpLong <- 
  gdp %>% 
  pivot_longer(!c(country, indicator),
               names_to = "year",
               values_to = "gdp") %>% 
  mutate( year = as.numeric(year))
gdpLong %>% 
  head(10)
```
```{r}
p <- data.frame(pregnate= c("yes", "no"),
                male= c(NA, 25),
                female= c(11, 18))
p
```
```{r}
pl <- p %>% 
  pivot_longer(c(male, female),
               names_to = "sex",
               values_to = "count")
pl
```
```{r}
pl %>% 
  pivot_wider(id_cols = pregnate, 
              names_from = sex,
              values_from = count)
```


